---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# decayr
[![Travis-CI Build Status](https://travis-ci.org/njtierney/decayr.svg?branch=master)](https://travis-ci.org/njtierney/decayr)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/decayr/master.svg)](https://codecov.io/github/njtierney/decayr?branch=master)

The goal of decayr is to demonstrate the use of a niche gaussian decay function, for the purposes of demonstrating how to use GitHub when making an R package.

## Installation

You can install decayr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("njtierney/decayr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(decayr)

gauss_decay(d_kj = 99,
            d_0 = 100)

gauss_decay(d_kj = 1,
            d_0 = 100)

```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
